High-Dimensional Regularized Discriminant Analysis

### 2015-10-25 reports/paper-hdrda.Rnw
Rewrote the beginning of simulation intro

% TODO: Combine first two paragraphs -- list R package along with authors

In this section, we compare our proposed classifier with four classifiers
recently proposed for small-sample, high-dimensional data. Our
competitors include shrunken centroids regularized discriminant analysis from
\cite{Guo:2007te} and penalized linear discriminant analysis from
\cite{Witten:2011kc}.

We used the implementations of the Witten and Guo
classifiers from the {\tt penalizedLDA} and {\tt rda} packages, respectively.
Because the {\tt rda} package does not perform the authors' ``Min-Min'' rule
automatically, we applied this rule within our {\tt R} code.

We also consider two modifications of diagonal linear discriminant analysis from
\cite{Tong:2012hw} and \cite{Pang:2009ik}, where the former employs an improved
mean estimator and the latter utilizes an improved variance estimator. We also
utilized the implementations of the Pang and Tong classifiers available in the
{\tt sparsediscrim} package.

We also included the random forest from \cite{Breiman:2001fb} as a benchmark
based on the findings of \cite{FernandezDelgado:2014ul}, who has concluded that
the random forest is often superior to other classifiers in benchmark studies.
We used the implementation of the random-forest classifier from the {\tt
  randomForest} package with 250 trees and 100 maximum nodes.

For each classifer we explicitly set prior probabilities as equal if
applicable. All other classifier options were set to their default settings.
We used version 3.2.2 of the open-source statistical software {\tt R} for the
classification study.  Below, we refer to each classifier by the first author's
surname.

For the \emph{HDRDA} classifier in \eqref{eq:hdrda-decomposed}, we examine the
classification performance of two models. For the first \emph{HDRDA} model, we
set $\alpha_k = 1$, $k = 1, \ldots, K$, so that the covariance-matrix estimator
\eqref{eq:hdrda-cov} employed resembled \eqref{eq:ridge-estimator}. We estimated
$\lambda$ from a grid of 21 equidistant candidate values between 0 and 1,
inclusively. Similarly, we estimated $\gamma$ from a grid consisting of the
values $10^{-1}, \ldots, 10^4$, and $10^5$. We selected optimal estimates of
$\lambda$ and $\gamma$ using $V$-fold cross-validation with $V = 10$
\citep{Hastie:2008dt}. For the second model, we set $\alpha_k = 1 - \gamma$, $k
= 1, \ldots, K$, to resemble \citeauthor{Friedman:1989tm}'s parameterization. We
estimated both $\lambda$ and $\gamma$ from a grid of 21 equidistant candidate
values between 0 and 1, inclusively.

>>>>

In this section, we compare our proposed classifier with four classifiers
recently proposed for small-sample, high-dimensional data along with the random
forest from \cite{Breiman:2001fb} using version 3.2.2 of the open-source
statistical software {\tt R}. Within our study, we included penalized linear
discriminant analysis from \cite{Witten:2011kc}, implemented in the {\tt
  penalizedLDA} package. We also considered shrunken centroids regularized
discriminant analysis from \cite{Guo:2007te} in the {\tt rda} package. Because
the {\tt rda} package does not perform the authors' ``Min-Min'' rule
automatically, we applied this rule within our {\tt R} code. We included two
modifications of diagonal linear discriminant analysis from \cite{Tong:2012hw}
and \cite{Pang:2009ik}, where the former employs an improved mean estimator and
the latter utilizes an improved variance estimator. Both classifiers are
available in the {\tt sparsediscrim} package. Finally, we incorporated the
random forest as a benchmark based on the findings of
\cite{FernandezDelgado:2014ul}, who concluded that the random forest is often
superior to other classifiers in benchmark studies. We used the implementation
of the random-forest classifier from the {\tt randomForest} package with 250
trees and 100 maximum nodes. For each classifer we explicitly set prior
probabilities as equal, if applicable. All other classifier options were set to
their default settings. Below, we refer to each classifier by the first
author's surname.

For the \emph{HDRDA} classifier in \eqref{eq:hdrda-decomposed}, we examined the
classification performance of two models. For the first \emph{HDRDA} model, we
set $\alpha_k = 1$, $k = 1, \ldots, K$, so that the covariance-matrix estimator
\eqref{eq:hdrda-cov} resembled \eqref{eq:ridge-estimator}. We estimated
$\lambda$ from a grid of 21 equidistant candidate values between 0 and 1,
inclusively. Similarly, we estimated $\gamma$ from a grid consisting of the
values $10^{-1}, \ldots, 10^4$, and $10^5$. We selected optimal estimates of
$\lambda$ and $\gamma$ using $V$-fold cross-validation with $V = 10$
\citep{Hastie:2008dt}. For the second model, we set $\alpha_k = 1 - \gamma$, $k
= 1, \ldots, K$, to resemble \citeauthor{Friedman:1989tm}'s
parameterization. We estimated both $\lambda$ and $\gamma$ from a grid of 21
equidistant candidate values between 0 and 1, inclusively.
